---
title: "20180313_three_function_overview"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
library(stringi)
library(refnet)
```


`references<-references_read()`

`authors<-authors_clean(references, sim_score=0.9)`

At this stage you go through and change any incorrectly grouped authors groupID to their authorID.

This function takes those changes and makes the names all the same, filters again, and makes some small changes and deletes some columns for input to your functions

`authors_final<-authors_refine(authors, sim_score=0.94)`

```{r, message=FALSE, eval=FALSE}



################
# EB TEST
################

eb_references <- references_read("~/refnet_materials/data/EBpubs.txt", dir=FALSE, filename_root="~/refnet_materials/output/eb")

eb_authors <- authors_clean(eb_references, filename_root="~/refnet_materials/output/eb")

eb_refined <- authors_refine(authors=eb_authors$authors, master=eb_authors$master)

save(eb_refined, file="~/refnet_materials/output/eb_refined.Rdata")

eb_georef <- authors_georef(ebreduced)



plot_addresses_country(data=eb_georef$addresses)
plot_addresses_points(data=eb_georef$addresses)
plot_net_address(data=eb_georef$addresses)
plot_net_coauthor(data=eb_georef$addresses)
plot_net_country(data=eb_georef$addresses)
```



```{r}
########
# LARR
########

LARR_references <- references_read("~/refnet_materials/data/LARR/", 
                                   dir=TRUE, 
             filename_root="~/refnet_materials/output/LARR")

LARR_authors <- authors_clean(LARR_references, filename_root="~/refnet_materials/output/LARR")

LARR_refined <- authors_refine(authors=LARR_authors$authors, master=LARR_authors$master)

save(LARR_refined, file="~/refnet_materials/output/LARR_refined.Rdata")

LARR_georef <- authors_georef(data=LARR_refined)

save(LARR_georef, file="~/refnet_materials/output/LARR_georef.Rdata")

plot_addresses_country(data=LARR_georef)
plot_addresses_points(data=LARR_georef)
plot_net_address(data=LARR_georef)
plot_net_coauthor(data=LARR_georef)
plot_net_country(data=LARR_georef)

################
# WOS 2018 TEST
################

WOS18_references <- references_read("~/refnet_materials/data/WOS2018/", 
              dir=TRUE, 
              filename_root="./output/WOS18")

WOS18_authors <- authors_clean(WOS18_references, filename_root="~/refnet_materials/output/WOS18")

WOS18_refine <- authors_refine(authors=WOS18_authors$authors, master=WOS18_authors$master)

WOS18_georef <- authors_georef(data=WOS18_refine)

plot_addresses_country(data=WOS18_georef)
plot_addresses_points(data=WOS18_georef)
plot_net_address(data=WOS18_georef)
plot_net_coauthor(data=WOS18_georef)
plot_net_country(data=WOS18_georef)


################
# WOS 2011 TEST
################

WOS11_references <- references_read("~/refnet_materials/data/WOS2011", dir=TRUE, 
                                    filename_root="~/refnet_materials/output/WOS11")

WOS11_authors <- authors_clean(WOS11_references, filename_root="~/refnet_materials/output/WOS11")

WOS11_references <- authors_refine(authors=WOS11_authors$authors, master=WOS11_authors$master)

################
# ECOLOGY TEST
################

Ecology_references <- references_read("~/refnet_materials/data/Ecology.txt", dir=FALSE, filename_root="~/refnet_materials/output/Ecology")

Ecology_authors <- authors_clean(Ecology_references, filename_root="~/refnet_materials/output/Ecology")

Ecology_refined <- authors_refine(authors=Ecology_authors$authors, master=Ecology_authors$master)

save(Ecology_refined, file="~/refnet_materials/output/Ecology_refined.Rdata")

Ecology_georef <- authors_georef(ER)

save(Ecology_georef, 
file="~/refnet_materials/output/Ecology_georef.Rdata")

plot_addresses_country(data=Ecology_georef$addresses)
#b <- plot_addresses_points(data=Ecology_georef$addresses)
#d <- plot_net_address(data=Ecology_georef$addresses)
#plot_net_coauthor(data=Ecology_georef$addresses)
#plot_net_country(data=Ecology_georef$addresses)


################
# BITR TEST
################


BITR_references <- references_read("~/refnet_materials/data/BITR", dir=TRUE, filename_root="~/refnet_materials/output/BITR")

BITR_authors <- authors_clean(BITR_references, filename_root="~/refnet_materials/output/BITR")

BITR_refined <- authors_refine(authors=BITR_authors$authors, master=BITR_authors$master)

save(BITR_refined, file="~/refnet_materials/output/BITR_refined.Rdata")

authors_georef(BITR_refined)


```

```{r}
load("~/refnet_materials/output/eb_refined.Rdata")



dat <- separate(data=eb_refined, col = address, 
         into=c("university","department","short_address"),
         sep=",",extra = "merge", remove=FALSE) %>%
       mutate(country=stri_extract_last_words(short_address),
        zip = str_extract(string=short_address, 
          pattern="[:digit:][:digit:][:digit:][:digit:][:digit:]"),
        city_state = str_extract(string=short_address,
                pattern="[:alnum:]{1,20}[,][ ][A-Z][A-Z]") ) %>%
      select(address, short_address, city_state, zip, country, university, department)

#write.csv(dat, file = "dat_parsed_addresses.csv")

```

\newpage

```{r}
head(dat[,c("address")])
head(dat[,c("university","department")])
head(dat[,c("short_address","city_state","zip","country")])
```